---
title       : Coursera Developing Data Products 
subtitle    : Course Assignment - Developing a Shiny App
author      : Xiangting
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

## Background 

My Shiny Application is based on the mtcars data set:

```{r,echo=FALSE}
data(mtcars)
```

A data frame with 32 observations on 11 variables. We are interested in the following 5 variables:

1. mpg        Miles/(US) gallon
2. cyl	Number of cylinders
3. hp	Gross horsepower
4. wt	Weight (lb/1000)
5. am	Transmission (0 = automatic, 1 = manual)

--- .class #id 

## Data Structure

Overview of the data structure

```{r}
head(mtcars)
```

--- .class #id 

## App Function

This app uses the mtcars dataset and allows users to predict Miles per gallon (MPG) using 4 variables - Horsepower, number of cylinders, weight and transmission (Automactic or Manual)

This is done through fitting a linear model on these 4 variables.  

```{r}
lm(mpg ~ hp + cyl + wt +am, data=mtcars)
```

--- .class #id 

## App Features

1. The radio buttons choices are use to limit inputs of number of cyliners and transmission to the valid inputs.  

2. Inputs of the users are shown for validation. 

3. The linear model function is used to predict the mpg based on the 4 variables input by the user. 

4. MPG is recalculated and displayed each time user changes a variable.

--- .class #id 

## Interactive Graphs

The app will also produce interactive graphs to show how MPG is related to the 4 variables.

```{r,echo=FALSE}
par(mfrow = c(1, 4))
                        # (1, 1)
                        with(mtcars, plot(hp, mpg,
                                          xlab='Gross horsepower',
                                          ylab='MPG',
                                          main='MPG vs horsepower'))
                                 
                        # (1, 2)
                        with(mtcars, plot(cyl, mpg,
                                          xlab='Number of cylinders',
                                          ylab='MPG',
                                          main='MPG vs cylinders'))
                        # (1, 3)
                        with(mtcars, plot(wt, mpg,
                                          xlab='Weight (lb/1000)',
                                          ylab='MPG',
                                          main='MPG vs weight'))
                        
                        # (1, 4)
                        with(mtcars, plot(am, mpg,
                                          xlab='Transmission (Automactic or Manual)',
                                          ylab='MPG',
                                          main='MPG vs Transmission'))
```     

